About

### 2020-08-05 analysis/about.Rmd
workflowr::wflow_publish("analysis/about.Rmd")

Target `defoliation_maps_wfr` builds are targets necessary for the final results [report](https://2019-feature-selection.pjs-web.de/report-defoliation.html).

@@

See the [`code`](https://github.com/pat-s/paper_hyperspectral/tree/master/analysis) directory on GitHub for the source code that generated the figures and statistical results contained in the manuscript.
See the [`data`](https://github.com/pat-s/paper_hyperspectral/tree/master/analysis/data) directory for instructions how to access the raw data discussed in the manuscript.

@@

This repository is organized as an R package, providing functions and raw data to reproduce and extend the analysis reported in the publication.
Note that this package has been written explicitly for this project and may not be suitable for more general use.

@@

* The organisation of this compendium is based on the work of [Carl Boettiger](http://www.carlboettiger.info/) and [Ben Marwick](https://github.com/benmarwick).

>>>>

Target `defoliation_maps_wfr` builds subsequent argets which are necessary for the final results [report](https://pat-s.github.io/2019-feature-selection/report-defoliation.html).

@@

See the [`code`](https://github.com/pat-s/paper_hyperspectral/tree/master/analysis) directory on GitHub for the source code that generated the figures and statistical results contained in the manuscript.
See the [`data`](https://github.com/pat-s/paper_hyperspectral/tree/master/analysis/data) directory for instructions how to access the raw data used in the manuscript.

@@

This repository is organized as an R package, providing functions and raw data to reproduce and extend the analysis reported in the publication.
Note that this package has been written explicitly for this project and is not suited a for more general use.

@@

* The organisation of this compendium was inspired by the works of [Carl Boettiger](http://www.carlboettiger.info/) and [Ben Marwick](https://github.com/benmarwick).
